Performance benefits of Intel Optane DC storage for the parallel processing of large neuroimaging data

### 2019-11-21 paper.tex
cleanup/changes in paper re results/modifications to figure generating scripts

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\algnewcommand\algorithmicforeach{\textbf{for each}}
\algdef{S}[FOR]{ForEach}[1]{\algorithmicforeach\ #1\ \algorithmicdo}
\algblock{Input}{EndInput}
\algnotext{EndInput}
\algblock{Output}{EndOutput}
\algnotext{EndOutput}
\newcommand{\Desc}[2]{\State \makebox[2em][l]{#1}#2}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage[binary-units]{siunitx}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\newcommand{\bigdata}{Big Data\xspace}
\newcommand{\bigbrain}{BigBrain\xspace}

@@

The server used in our experiments contain $\SI{3}{\tera\byte}$ of Intel Optane Persistent memory, 768GB of DRAM,
Isilon, local disk(SSD).
CPU: Cascade lake
OS: Red Hat 7.1
writeback enabled for local disk (unsure about Isilon)
\valerie{include storage bandwidth table here}

@@

Memory Mode allows Intel Optane DC persistent memory to extend the system's available
memory. In this mode, Optane uses DRAM as a cache and Optane can be accessed as
volatile addressable main memory. By extending main memory, Memory Mode enables the
fast access of large volumes of data.

As Memory Mode would affect the processing time regardless of the device
selected, we evaluated Memory Mode on tmpfs, local disk and Isilon. tmpfs
consisted of $\SI{298}{\giga\byte}$ and was located in \texttt{/run/user/61218}.
Local disk comprised of a $\SI{240}{\giga\byte}$ Micron 5100 PRO SSD, of which
$\SI{150}{\giga\byte}$ were mounted on \texttt{/home}. The $\SI{628}{\tera\byte}$
Isilon was mounted as NFS4 to \texttt{/home/users}

Optane was not evaluated separately as it is indistinct from DRAM memory in
Memory Mode
\subsubsection{App Direct Mode}

App Direct Mode enables Optane to be accessed as a high-performance storage device.
Unlike Memory Mode, the OS is able to differentiate between main memory and Optane
storage, treating them as two distinct entities. As Optane is located on
the DIMMs, it exhibits lower latencies than traditional SSDs, while being able
to be accessed like an SSD. Optane does not use the DRAM as cache in App Direct Mode.

The same storage devices were used to evaluate App Direct Mode, with the inclusion
of Intel Optane DC Persistent Memory, of which $\SI{1.5}{\tera\byte}$ of storage
were mounted on \texttt{/pvme-1}.

@@

For the purposes of these experiments, we use the inequality introduced in
\cite{paperinmem} to characterize data-intensive applications. That is,
\begin{equation}                                                                 
\frac{D}{C} \leq \frac{\delta}{\gamma} \label{eq:page-cache-inequality}                                                                                                                                  
\end{equation} 
where:
\begin{itemize}
    \item $D$ is the total amount of data written by the application
    \item $C$ is the total execution time of the application
    \item $\delta$ is the disk bandwidth
    \item $\gamma$ is the max number of concurrent processes on a node
\end{itemize}

Using this inequality, we anticipate that whenever the application is within the limits,
the storage selection will make little difference, as storage devices with writeback enabled 
will be able to leverage the memory cache. It is expected that Optane in App Direct Mode
will be most useful when this inequality is not satisfied as storage devices will
not be able to use the writeback cache. As Memory Mode will inevitably
increase the amount of data that can be cached by the storage, it is expected that the overall
performance of all storage devices improve, even when the inequality is not satisfied.

@@

\begin{algorithm}\caption{Incrementation}\label{alg:incrementation}
    \begin{algorithmic}[1]
    \Input
        \Desc{$x$}{a sleep delay in seconds}
        \Desc{$n$}{a number of iterations}
        \Desc{$C$}{a set of image chunks}
        \Desc{$fs$}{filesystem to write to (tmpfs, Optane, local disk, Isilon)}
    \EndInput
    \ForEach{$chunk \in C$}
        \State read $chunk$ from $fs$
        \For{$i \in [1, n]$}
            \State $chunk\gets chunk+1$
            \State sleep $x$
        \EndFor
        \State save $chunk$ to $fs$
    \EndFor
    \end{algorithmic}
\end{algorithm}

Due to the size and uniqueness of the \bigbrain, standardized processing pipelines
have yet to be developed for it. In order to quantify the effects of data location
on such a dataset, we have implemented a naive synthetic application that takes 
the image, split into blocks, and increments all the voxels within each block, in parallel (Algorithm~\ref{alg:incrementation}).
This application
enables us to read and write to different storage devices and ensure that written
data could not have been previously cache
in-memory, by ensuring that read and written data are not the same. This application
was parallelized us in two different ways: using both GNU Parallel and Apache Spark 2.4.3 (PySpark). 
All task code was implemented in Python 3.6 \tristan{In a subsequent 
version you could give more details about implementations, including containerization, etc}. While the GNU Parallel application
is currently limited to 1 incrementation step, the Apache Spark implementation allows us to increase
the number of incrementation steps by a variable amount, thereby increasing the amount of intermediate
data generated.

Time is measured within the application using Python's \texttt{time} module 
called before and after any reads, increments or writes.

We have executed this pipeline on both the $\SI{76}{\gibi\byte}$ 40~$\mu$m 
\bigbrain split into 125 $\SI{617}{\mega\byte}$ blocks and the $\SI{603}{\gibi\byte}$
\bigbrain at 20~$\mu$m split into 1000 $\SI{617}{\mebi\byte}$ blocks.

For the 40~$\mu$m \bigbrain, we have executed the application using GNU Parallel for parallelization
using 25 and 96 processes on the 125 40$\mu$m \bigbrain blocks. Data was read and written to either
tmpfs, Optane (App Direct only), local disk and Isilon. In all configurations (25 and 96 processes)
only 1 iteration was performed. At 25 processes, a sleep delay of 120 seconds was added at the
incrementation step, which would emulate tasks of longer duration and ensure that we satisfy Equation~\ref{eq:page-cache-inequality} for all devices.
At 96 processes with 0 sleep delay, we estimate being above the inequality for local disk and Isilon.
All experiments were repeated 5x in each environment (App Direct and Memory Mode).

For the 20~$\mu$m \bigbrain, we used the same application, however in this case, it was executed
using both Apache Spark and GNU Parallel. The configuration was also generally the same, having 
experiments using both 25 and 96 cpus. As the previous experiments would have already shown how
page cache availability for the dirty writes can compare with Optane, we did not include
a task duration delay. Rather, we just measure the performance differences between the various
storage devices, in addition to comparing how each device scales by modifying the cluster size.

Since storage was limited on tmpfs and local disk and was not large enough to process the entire
20~$\mu$m \bigbrain, we had to emulate the reading and writing to these devices. We achieved this
by copying only 70 of the 1000 blocks onto the storage devices, but used 1000 tasks to read, increment and
write these 70 blocks.

@@

The BIDS App Example is a template example for creating a Brain Imaging Data Structure (BIDS)
compliant application. It runs a standard neuroimaging brain extraction application (FSL BET) 
on all the anatomical (T1W) images of a dataset containing numerous subjects. This step is 
referred to as Participant analysis, within the BIDS App Example. An optional
step of the BIDS App example, referred to as Group analysis, computes the average brain
mask size of the entire dataset.

For our experiments, we used the entire CoRR dataset, made available on DataLad and
applied Participant analysis on it. As in the BigBrain Incrementation, the experiment parallelized 
using GNU Parallel with 25 and 96 processes. The conditions were executed in both App Direct and Memory Mode
using Isilon, local disk, Optane and tmpfs as storage. As participant analysis operates on only a subset of the dataset,
the inequality is satified for all conditions. Each experiment was repeated 3x.

@@

\subsection{40~$\mu$m \bigbrain incrementation}
\subsubsection{25 Processes}
\begin{figure}
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/makespan-real-25cpus-120delay-1it.pdf}
    \captionsetup{width=\columnwidth}
    \caption{Makespan of \bigbrain Incrementation using 25 processes with a sleep delay of 120s on 125 blocks on the 40~$\mu$m image given different storage configurations. 5 repetitions were performed.}\label{fig:makespan-25cpus}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/stacked-real-25cpus-120delay-1it.pdf}
    \captionsetup{width=\columnwidth}
    \caption{Total read/increment/write breakdown of \bigbrain Incrementation using 25 processes with a sleep delay of 120s on 125 blocks on the 40~$\mu$m image given different storage configurations. 5 repetitions were performed.}\label{fig:stacked-25cpus}
\end{figure}
\begin{figure*}
    \begin{subfigure}{\columnwidth}
        \centering
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/gantt-1567709282-tmpfsAD_1it_25cpus_120delay_withpc-2.pdf}
    \caption{tmpfs}
\end{subfigure}
\begin{subfigure}{\columnwidth}
        \centering
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/gantt-1567705458-optaneAD_1it_25cpus_120delay_withpc-2.pdf}
    \caption{Optane}
\end{subfigure}
\begin{subfigure}{\columnwidth}
        \centering
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/gantt-1567704324-localAD_1it_25cpus_120delay_withpc-2.pdf}
    \caption{local disk}
\end{subfigure}
\begin{subfigure}{\columnwidth}
        \centering
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/gantt-1567707833-isilonAD_1it_25cpus_120delay_withpc-2.pdf}
    \caption{Isilon}\label{fig:gantt25isilon}
\end{subfigure}
\caption{Gantt charts for each storage device (App Direct Mode) processing 125 blocks of the 40$\mu$m BigBrain using 25 processes and a sleep delay of 120s}\label{fig:gantt25}
\end{figure*}

As shown in Figure~\ref{fig:makespan-25cpus}, despite being under the inequality, the
performance still varies according to selected storage device. As expected, Optane performs
slightly better than local disk and significantly better than Isilon. Tmpfs outperforms all
devices, with only slightly better performance than Optane and local disk, in both App Direct Mode and Memory Mode.
There is no apparent difference between the two modes on the given devices.

@@

Memory mode was found to result in increased computation time. When processing 
the 20~$\mu$m \bigbrain, Memory mode results indicate that more time was spent on
the incrementation tasks than its App Direct counterparts. Unlike App Direct mode,
which relies exclusively on DRAM for working memory, Memory mode relies on Optane
with a DRAM cache. Optane, while faster than other persistent storage devices, 
still lacks the bandwidth of DRAM. Should anonymous memory need to access Optane
for computation, it is not surprising that it would be slower than a DRAM-only
access. However, whereas Memory mode experienced increased computation during the
processing of the 20~$\mu$m \bigbrain, this was not always found to be the case
with the processing of the 40~$\mu$m \bigbrain. In fact, incrementation time was
largely similar between the two modes, with the notable exception of Optane in
Memory mode expending significantly less computation time than in App Direct when
processing the 40~$\mu$m \bigbrain with both 25 and 96 processes. Optane in 
Memory mode executing on local disk using 96 cpus, however, required significant
computation time as compared to App Direct. 
- Conclusion: memory mode should only be used when there's a requirement for additional memory
-App Direct mode results in increased I/O time for Optane
- conclusion: Optane might benefit from the DRAM cache

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\algnewcommand\algorithmicforeach{\textbf{for each}}
\algdef{S}[FOR]{ForEach}[1]{\algorithmicforeach\ #1\ \algorithmicdo}
\algblock{Input}{EndInput}
\algnotext{EndInput}
\algblock{Output}{EndOutput}
\algnotext{EndOutput}
\newcommand{\Desc}[2]{\State \makebox[2em][l]{#1}#2}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage{multirow}
\usepackage[binary-units]{siunitx}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\newcommand{\bigdata}{Big Data\xspace}
\newcommand{\bigbrain}{BigBrain\xspace}

@@

The server used for the experiments consisted of 12 \SI{64}{\gibi\byte} DRAM devices,
resulting in a total of \SI{768}{\gibi\byte} of DRAM, and 12 \SI{256}{\giga\byte} Intel Optane DC Memory
devices, resulting in total of \SI{3}{\tebi\byte} of Intel Optane DC Memory. The theoretical maximum bandwidth
of DRAM is estimated to be around \SI{275}{\gibi\byte}~/s whereas for Optane, it is
estimated to be around \SI{250}{\gibi\byte}~/s.
Other storage devices included a \SI{240}{\gibi\byte} Micron SATA SSD, of which
only \SI{149}{\gibi\byte} where available for the experiments, and a \SI{628}{\tebi\byte} shared Dell EMC Isilon cluster. The local disk
was the only storage device set up as a writeback device. Both Isilon and Optane in
App Direct mode were configured as write-through devices, meaning they did not leverage
DRAM as a cache for writes. This was achieved in Optane by configuring the xfs filesystem with
DAX. All storage devices were benchmarked using the following \href{https://github.com/ValHayot/paper-memory-storage/scripts/bench_disks.sh}{script}.
The result of the benchmarks can be seen in Table \ref{table:bandwidths}.

For processing,
2 Intel(R) Xeon(R) Platinum 8260M CPU @ 2.40GHz where installed, enabling use of up to 96 threads.
The server was running Red Hat Enterprise Linux 7.6 release (Maipo).

\begin{table}
\begin{center}
 \begin{tabular}{ |c|c|c| } 
     \cline{2-3}
     \multicolumn{1}{c|}{} & \multicolumn{2}{c|}{Bandwidth (MB/s)} \\\hline
  Device & Read & Write \\
 \hline
 DRAM & 5304.3 & 3338.2 \\  
 Optane & 3379.2 & 2396.2 \\   
 Local Disk & 518.6 & 240.4 \\
 Isilon & 117.0 & 111.8 \\
 \hline
\end{tabular}\caption{Perceived read and write bandwidth of each storage device}\label{table:bandwidths}
\end{center}
\end{table}

@@

Memory Mode leverages Intel Optane DC persistent memory (Optane) to extend the system's available
memory. In this mode, Optane uses DRAM as a cache and is accessible as
volatile addressable main memory. By extending main memory, Memory Mode enables the
fast access of large volumes of data.

While enabling the access to larger amount of memory than typically accessible otherwise,
it is anticipated that Memory Mode will be slower than AD mode for all memory accessed that
are not cached in DRAM. We evaluated all available devices (Optane through tmpfs, local disk and Isilon)
in Memory Mode.

\subsubsection{App Direct Mode}

App Direct Mode enables Optane to be accessed as a high-performance storage device.
Unlike Memory Mode, the OS is able to differentiate between DRAM and Optane,
treating them as two distinct entities. As Optane is located on
the DIMMs, it exhibits lower latencies than traditional SSDs, while being able
to be accessed like an SSD. Optane does not use the DRAM as cache in App Direct Mode
if configured with DAX.

Similarly to Memory Mode, our experiments evaluated all available filesystems in App Direct
Mode. In other words, we evaluated DRAM performance through tmpfs, Optane performance through
a \SI{1.5}{\tebi\byte} Intel Optane DC Persistent Memory storage device and local disk
and Isilon using the same storage mounts available in Memory Mode.

@@

We characterize the performance of our experiments using the following model:

\begin{equation}
    M \geq \frac{D}{R} + \frac{D}{W} \label{eq:makespan}
\end{equation}

where,
\begin{itemize}
        \item $M$ is the application makespan
        \item $D$ is the total amount of data processed by the application
        \item $R$ is the device read bandwidth
        \item $W$ is the device write bandwidth
\end{itemize}

For applications which have negligible CPU time, as is the case with our experiments, 
it is expected that the I/O duration can estimate the total makespan. However, there
are certain instances where the makespan may be below the I/O duration. This is expected
to occur with storage devices that scale well with increased parallelism, as should be the
case for DRAM, Optane and Isilon, which all consist of multiple devices. Should the
scalable storage devices predict the makespan accurately, it is believed that other overheads
would be at play making the device unfavourable for parallel processing.

@@

\begin{algorithm}\caption{Incrementation}\label{alg:incrementation}
    \begin{algorithmic}[1]
    \Input
        \Desc{$x$}{a sleep delay in seconds}
        \Desc{$n$}{a number of iterations}
        \Desc{$C$}{a set of image chunks}
        \Desc{$fs$}{filesystem to write to (tmpfs, Optane, local disk, Isilon)}
    \EndInput
    \ForEach{$chunk \in C$}
        \State read $chunk$ from $fs$
        \State $chunk\gets chunk+1$
        \State save $chunk$ to $fs$
    \EndFor
    \end{algorithmic}
\end{algorithm}

Due to the size and uniqueness of the \bigbrain, standardized processing pipelines
have yet to be developed. In order to quantify the effects of storage devices
on such a dataset, we have implemented a naive synthetic application that takes 
the image, split into blocks, and increments all the voxels within each block, in parallel (Algorithm~\ref{alg:incrementation}).
This application
enables us to read and write to different storage devices and ensure that written
data could not have been previously cache
in-memory, by ensuring that read and written data are not the same. This application
was parallelized us in two different ways: using both GNU Parallel and Apache Spark 2.4.3 (PySpark). 
All code was implemented in Python 3.6.

Time is measured within the application using Python's \texttt{time} module 
called before and after any read and writes.

We have executed this pipeline on both the $\SI{75}{\gibi\byte}$ 40~$\mu$m 
\bigbrain split into 125 $\SI{614}{\mebi\byte}$ blocks and the $\SI{603}{\gibi\byte}$
\bigbrain at 20~$\mu$m split into 1000 $\SI{617}{\mebi\byte}$ blocks.

For the 40~$\mu$m \bigbrain, we have executed the application using GNU Parallel for parallelization
using 25 and 96 processes on the 125 40$\mu$m \bigbrain blocks. Data was read and written to either
DRAM (App Direct only), Optane, local disk and Isilon.

For the 20~$\mu$m \bigbrain, we used the same application, however in this case, it was executed
using both Apache Spark and GNU Parallel. The configuration was also generally the same, having 
experiments using both 25 and 96 cpus. Repeating the experiments using a larger dataset would enable
us to determine the effects when Optane would have to be partially relied upon due to insufficient DRAM
space. Moreover, with such large datasets, it is likely that Big Data frameworks would be used rather than
more traditional parallelism frameworks. Using Spark, we can evaluate how Big Data Frameworks perform on
different storage devices.

Since storage was limited on DRAM and local disk and was not large enough to process the entire
20~$\mu$m \bigbrain, these devices were omitted in the processed of this dataset.

@@

The BIDS App Example is a template example for creating a Brain Imaging Data Structure (BIDS)
compliant application. It runs a standard neuroimaging brain extraction application (FSL BET) 
on all the anatomical (T1W) images of dataset containing numerous subjects. This step is 
referred to as Participant analysis within the BIDS App Example. An optional
step of the BIDS App example, referred to as Group analysis, computes the average brain
mask size of the entire dataset.

For our experiments, we used the entire CoRR dataset, made available on \href{}{DataLad} and
applied Participant analysis to it. The BIDS App Example was executed using a Singularity container stored on
Isilon. As in the BigBrain Incrementation, the experiment parallelized 
using GNU Parallel with 25 and 96 processes. The conditions were executed in both App Direct and Memory Mode
using Isilon, local disk and Optane as storage. Each experiment was repeated 3x.

@@

\subsection{40~$\mu$m \bigbrain incrementation}
\subsubsection{25 Processes}
\begin{figure}
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/makespan-real-40bb_25cpu.pdf}
    \captionsetup{width=\columnwidth}
    \caption{Makespan of the \bigbrain Incrementation application using 25 
             processes on the 125 blocks on the 40~$\mu$m image given different
             storage configurations. Anticipated read and write duration was 
             measured by applying the perceived bandwidths Table~\ref{table:bandwidths}
             to Eq.~\ref{eq:makespan}. 3 
             repetitions were performed. *Local SSD did not complete the
    writing of the last few blocks due to storage limitations.}\label{fig:makespan-25cpus}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/violin-read-20bb_25cpu.pdf}
    \captionsetup{width=\columnwidth}
    \caption{Total read/increment/write breakdown of \bigbrain Incrementation using 2. 3 repetitions were performed.}\label{fig:stacked-25cpus}
\end{figure}
\begin{figure*}
    \begin{subfigure}{\columnwidth}
        \centering
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/gantt-1567709282-tmpfsAD_1it_25cpus_120delay_withpc-2.pdf}
    \caption{tmpfs}
\end{subfigure}
\begin{subfigure}{\columnwidth}
        \centering
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/gantt-1567705458-optaneAD_1it_25cpus_120delay_withpc-2.pdf}
    \caption{Optane}
\end{subfigure}
\begin{subfigure}{\columnwidth}
        \centering
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/gantt-1567704324-localAD_1it_25cpus_120delay_withpc-2.pdf}
    \caption{local disk}
\end{subfigure}
\begin{subfigure}{\columnwidth}
        \centering
    \includegraphics[width=\columnwidth]{./experiments/bigbrain-incrementation/figures/gantt-1567707833-isilonAD_1it_25cpus_120delay_withpc-2.pdf}
    \caption{Isilon}\label{fig:gantt25isilon}
\end{subfigure}
\caption{Gantt charts for each storage device (App Direct Mode) processing 125 blocks of the 40$\mu$m BigBrain using 25 processes and a sleep delay of 120s}\label{fig:gantt25}
\end{figure*}

As can be seen in Figure~\ref{fig:makespan-25cpus}, DRAM (App Direct Mode) is the 
most efficient, with a makespan of 7.6s. Optane in Memory mode is a close second
with a makespan of approximately 10s. Optane in App Direct mode is approximately 
12x slower than Optane in Memory Mode. Isilon in both Memory Mode and App Direct 
Mode is more than 120x slower than Optane in Memory Mode. Other than for Optane, 
there is no significant difference between Memory Mode and App Direct executions.

When comparing the makespan to the estimated read and write duration, local SSD
in both modes and Optane in App Direct Mode have longer makespans than the anticipated.
Optane was approximately 2.2x slower than expected, whereas local SSD was approximately
1.4x slower than expected, in both modes. For those where the I/O time was overestimated,
DRAM was almost 5x faster in reality compared to what was estimated. Optane in Memory Mode
had a smaller difference, with it being 3.8x faster than expected. Isilon in App Direct
mode had a larger difference than Memory mode, with it being 1.1x faster than expected.

@@

Memory mode was found to result in increased computation time. When processing 
the 20~$\mu$m \bigbrain, Memory mode results indicate that more time was spent on
the incrementation tasks than its App Direct counterparts. Unlike App Direct mode,
which relies exclusively on DRAM for working memory, Memory mode relies on Optane
with a DRAM cache. Optane, while faster than other persistent storage devices, 
still lacks the bandwidth of DRAM. Should anonymous memory need to access Optane
for computation, it is not surprising that it would be slower than a DRAM-only
access. However, whereas Memory mode experienced increased computation during the
processing of the 20~$\mu$m \bigbrain, this was not always found to be the case
with the processing of the 40~$\mu$m \bigbrain. In fact, incrementation time was
largely similar between the two modes, with the notable exception of Optane in
Memory mode expending significantly less computation time than in App Direct when
processing the 40~$\mu$m \bigbrain with both 25 and 96 processes. Optane in 
Memory mode executing on local disk using 96 cpus, however, required significant
computation time as compared to App Direct mode. For all GNU Parallel runs, the 
read only consisted of loading metadata into
- Conclusion: memory mode should only be used when there's a requirement for additional memory
-App Direct mode results in increased I/O time for Optane
- conclusion: Optane might benefit from the DRAM cache
